---
title: "AS03_join_edu_data"
author: "B06208030 Wayne Ho"
date: "10/15/2019"
output:
  html_document:
    highlight: zenburn
    number_sections: no
    theme: cerulean
    toc: yes
    css: style.css
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```


```{r}
library(tidyverse)
options(stringsAsFactors = F)
```

# Q1 Joining educational data
- Reading educational data from the following csv file.

## Reading education data
```{r}
read_csv("data/opendata107Y020.csv") %>%
    slice(-1) %>% 
    glimpse()
```


## Town level educational data 
- Original data is village-level data
- Following In-Class tutorial, using `group_by()` to create town-level statistical data.

```{r, message=FALSE, warning=FALSE}
# exception handler
education_contains_two <- read_csv("data/opendata107Y020.csv") %>%
  slice(-1) %>%
  filter(str_detect(site_id, "一$|二$")) %>%
  mutate(site_id = str_replace_all(site_id, "一|二", "區"))

# load education
education <- read_csv("data/opendata107Y020.csv") %>%
  slice(-1) %>%
  filter(!str_detect(site_id, "一$|二$")) %>%
  rbind(education_contains_two) %>%
  gather(key = "key", value = "value", -c(statistic_yyy, district_code, site_id, village)) %>%
  select(site_id, key, value) %>%
  separate(col = "key", into = c("edu", "level", "state", "gender"), sep = "_") %>%
  select(-edu)

# exception for illiterate
education_illiterate <- education %>%
  filter(level == "illiterate" | level == "selftaughtl") %>%
  mutate(gender = state,
         state = NA)

education.tidy <- education %>%
  filter(level != "illiterate" && level != "selftaughtl") %>%
  rbind(education_illiterate) %>%
  filter(!str_detect(level, "age")) %>%
  mutate(value = as.numeric(value)) %>%
  group_by(site_id, level) %>%
  summarise(value = sum(value)) %>%
  ungroup() %>%
  spread(level, value) %>%
  mutate(all.people = rowSums(.[2:12]), 
         univ.people = rowSums(.[c(2,5,7,12)]),
         univPerc = univ.people / all.people)

education.tidy %>% head
```

## Loading town-level age, marriage, and referendum data
- Loading town-level data created in class

```{r,message=FALSE}
# exception handler
marriage_contains_two <- read_csv("data/population.csv") %>%
  filter(str_detect(site_id, "一$|二$")) %>%
  mutate(site_id = str_replace_all(site_id, "一|二", "區")) %>%
  group_by(site_id) %>%
  summarise(people = sum(people),
            elderSum = sum(elderSum),
            marriedSum = sum(marriedSum),
            elderPerc = elderSum / people,
            marriedPerc = marriedSum / people) %>%
  ungroup()

# load marriage
marriage <- read_csv("data/population.csv") %>%
  mutate(
    site_id = str_remove_all(site_id, "　")
  ) %>%
  filter(!str_detect(site_id, "一$|二$")) %>%
  rbind(marriage_contains_two)

# load ref10
ref10.raw <- read_csv("data/referendum_byTown/ref10.csv", locale = locale(encoding = 'UTF-8')) %>%
  slice(-1) 
names(ref10.raw) <- c("refno", "county", "town", "n_agree", "n_disagree", "n_valid", "n_invalid", "n_ticket", "n_people", "perc_ticket", "perc_agree", "perc_disagree", "agree_disagree")

ref10 <- ref10.raw %>%
  filter(!is.na(town)) %>%
  select(refno, county, town, n_agree, n_disagree, n_valid, n_invalid, n_ticket, n_people) %>%
  mutate(site_id = paste0(county, town)) %>%
  select(refno, site_id, everything()) %>%
  select(-c(county, town)) %>%
  group_by(refno, site_id) %>%
  summarise_all(.funs = sum) %>%
  ungroup() %>%
  mutate(perc_ticket = n_ticket / n_people,
         perc_agree = n_agree / n_ticket,
         perc_disagree = 1 - perc_agree)

marriage %>% head
ref10 %>% head

```



## Joining data together
- Joining all town-leave data together (Including new educational dada, and age, marriage, referendum data introduced in class)
```{r}

df <- ref10 %>%
  left_join(marriage, by = "site_id") %>%
  left_join(education.tidy, by = "site_id")

```

## **Q1 Ans: Joined data dimension**
- using `dim()` to display data dimension (should be 368). TAs will score Q1 according to the outcome.
```{r}

dim(df)

```


## **Q1 Ans: glimpse()**
- Using `glimpse()` to print out data you join below. TAs will score Q1 according to the `glimpse()` outcome.
```{r}

glimpse(df)

```

# Q2 Open Question - Joining one more dimension
- TASK: Collecting one more dimension from open data for town level and join it with the eucation, married, age, and referendum data.


## Read the file
```{r}

child <- read_csv("data/opendata107b040.csv")
population <- read_csv("data/population.csv") # in class

```

## Display the data dimension of the file
```{r}

dim(child)
dim(population)

```

## Add code chunks as you need

```{r}
# exception handler
child_contains_two <- child %>%
  slice(-1) %>%
  filter(str_detect(site_id, "一$|二$")) %>%
  mutate(site_id = str_replace_all(site_id, "一|二", "區"))

population_contains_two <- population %>%
  slice(-1) %>%
  filter(str_detect(site_id, "一$|二$")) %>%
  mutate(site_id = str_replace_all(site_id, "一|二", "區")) %>%
  select(site_id, people) %>%
  group_by(site_id) %>%
  summarise(people = sum(people))
  

# child data
tidy_child <- child %>%
  slice(-1) %>%
  filter(!str_detect(site_id, "一$|二$")) %>%
  rbind(child_contains_two) %>%
  select(site_id, birth_count) %>%
  mutate(birth_count = as.numeric(birth_count)) %>%
  group_by(site_id) %>%
  summarise(birth_count = sum(birth_count)) %>%
  ungroup()

# population data
tidy_population <- population %>%
  select(site_id, people) %>%
  filter(!str_detect(site_id, "一$|二$")) %>%
  rbind(population_contains_two)

# merge
df <- df %>%
  mutate(birth_rate = tidy_child$birth_count / tidy_population$people * 1000)
```


## **Q2 Ans: Answer following questions**
- Data source link (the page you download the data): 
- Describe the data source in your words: 
    
107年全臺各區嬰兒出生數: https://data.gov.tw/dataset/100324
    
    透過新生兒出生數與課堂計算之各區域總人口計算出生率CBR(每年、每一千人當中的新生人口數)做為一變數面向
    
## **Q2 Ans: Dim() of joined data frame**

```{r}
dim(df)
```


## **Q2 Ans: glimpse() of joined data frame**
```{r}
glimpse(df)
```

# Q3 Open question - Linear regression
 - Now, you have age, marriage, and education as indenpendent variables and referendum 10th agreement as the dependent variable.
 - Go online and search how to run regression with R
 - Report the regression result 

## **Q3 Ans**
```{r}

# Perc_agree & MarriedPerc
agree.marry <- lm(formula = perc_agree ~ marriedPerc, data = df)
summary(agree.marry)
cor.test(df$perc_agree, df$marriedPerc)

```

    公投第10案同意率與結婚比例回歸結果顯示：
    斜率為0.48590，截距為0.37413，
    通過顯著水準為0.001之假設檢定拒絕Ho，兩者關係為正相關
    由R-squared可以得知此回歸可以解釋約 11% 的變異
    相關係數為0.332713
    
```{r}

# Perc_agree & Education
agree.edu <- lm(formula = perc_agree ~ univPerc, data = df)
summary(agree.marry)
cor.test(df$perc_agree, df$univPerc)

```

    公投第10案同意率與大學畢業比例回歸結果顯示：
    斜率為-0.203672，截距為0.794034，
    通過顯著水準為0.001之假設檢定拒絕Ho，兩者關係為負相關
    由R-squared可以得知此回歸可以解釋約 39% 的變異
    相關係數為-0.6244475 
    
```{r}

# Perc_agree & BirthRate
agree.birth <- lm(formula = perc_agree ~ birth_rate, data = df)
summary(agree.birth)
cor.test(df$perc_agree, df$birth_rate)

```

    公投第10案同意率與107年出生率回歸結果顯示：
    斜率為-1.195 * 10^(-4)，截距為0.794034，
    通過顯著水準為0.001之假設檢定拒絕Ho，兩者關係為負相關
    由R-squared可以得知此回歸可以解釋約 5% 的變異
    相關係數為-0.2285568

# Q4 Challenge: The median of grouped data
- Calculating age median of grouped data
- Reference: https://www.themathdoctors.org/finding-the-median-of-grouped-data/
- Solve it wit dplyr pkgs
- If you can't answer the question correctly, keep your code (even wrong) to get partial scores.

```{r}

age <- read_csv("data/marriage.csv") %>%
  select(site_id, ageLower, ageUpper, value) %>%
  mutate(ageRange = str_c(ageLower, "~", ageUpper)) %>%
  select(site_id, ageRange, value)

# exception handler
age_contains_two <- age %>%
  filter(str_detect(site_id, "一$|二$")) %>%
  mutate(site_id = str_replace_all(site_id, "一|二", "區"))

age.368 <- age %>%
  filter(!str_detect(site_id, "一$|二$")) %>%
  rbind(age_contains_two) %>%
  group_by(site_id, ageRange) %>%
  summarise(value = sum(value)) %>%
  ungroup()

tidy.age <- data.frame()
tag <- age.368$site_id %>% unique()

# rearrange
for (i in tag) {
  
  age.temp <- age.368 %>%
    filter(site_id == i)
  
  age.temp <- rbind(age.temp[-2, ], age.temp[2, ])
  tidy.age <- rbind(tidy.age, age.temp)
  
}

head(tidy.age)


# find median range
df.median <- data.frame(
  group = character(),
  value = numeric(),
  value_sum = numeric(),
  median_position = character(),
  cumulative = numeric(),
  group_count = numeric()
)

for (i in tag) {
  
  age <- tidy.age %>% filter(site_id == i)
  
  index <- sum(age$value) / 2
  cumulative <- 0
  goal <- 0
  counter <- 1
  
  while (index > 0) {
    index <- index - age$value[counter]
    if (index > 0) {
      cumulative <- cumulative + age$value[counter]
      counter <- counter + 1
    } else{
      goal <- age$ageRange[counter]
    }
  }
  
  df.median <- rbind(
    df.median, 
    data.frame(
      tag = i,
      value = age$value[counter],
      value_sum = sum(age$value),
      median_position = goal,
      cumulative, 
      group_count = counter
    )
  )
}

# estimate median
L <- df.median %>%
  select(median_position) %>%
  separate(median_position, into = c("lower","upper"), sep = "~") %>%
  select("lower") %>%
  unlist %>%
  as.numeric()

df.median$est.median <- L + ((df.median$value_sum / 2) - df.median$cumulative) / df.median$value * 5
df.median
```



## **Q4 Ans: glimpse()**
```{r}
glimpse(df.median)
```

